Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-09 fib2.tex
anyon paths are red
more pictures

\section{Computation of logical operators}

Here we show a process where a 
tau anyon is wrapped around the torus twice.
The vertical lines represent a periodic
identification, and we leave anyons paths
as undirected because Fibonacci anyons are
self-inverse.
The dotted lines represent vacuum charges,
and we are free to include these lines or
not.
\begin{align*}
\includegraphics[]{pic-logops.pdf}
\end{align*}

@@

\section{Details on the algorithm}

>>>>

\section{Computation of homologically non-trivial operators}

Specializing to the Fibonacci case,
we write the non-trivial $F$-moves as the following
skein relations:
\begin{align*}
\includegraphics[]{pic-skein1.pdf}
\end{align*}

The sollid lines represent Fibonacci world-lines.
The dotted lines represent vacuum charges,
and we are free to include these lines or not.
The non-trivial $R$-moves are:
\begin{align*}
\includegraphics[]{pic-skein2.pdf}
\end{align*}

Removing bubbles:
\begin{align*}
\includegraphics[]{pic-bubble.pdf}
\end{align*}

Here we show a process where a 
Fibonacci anyon travels around the torus and
anihilates itself. Twice.
The vertical lines represent a periodic
identification, and we leave anyons paths
as undirected because Fibonacci anyons are
self-inverse.
\begin{align*}
\includegraphics[]{pic-logops.pdf}
\end{align*}

@@

\section{Details on the simulation algorithm}
